Competing Constructions for German Measure Noun Phrases: from Usage Data to Experiment

### 2017-04-06 Latex/article.tex
Even more DONEmake quick

  \author*[1]{Roland Schäfer}
  %\runningauthor{...}
  \affil[1]{Freie Universität Berlin}
  \title{Competing Constructions for German Measure Noun Phrases: from Usage Data to Experiment}
  \runningtitle{Competing Constructions for German Measure Noun Phrases}
  %\subtitle{...}
  \abstract{}
  \keywords{corpus methods and experimental methods, self-paced reading, forced choice, alternations, hierarchical models, measure constructions, German}
  %\classification[PACS]{...}
  %\communicated{...}
  %\dedication{...}
  %\received{...}
  %\accepted{...}
  \journalname{(submitted)}
  \journalyear{2017}
  %\journalvolume{...}
  %\journalissue{...}
  %\startpage{...}
  %\aop
  %\DOI{...}

@@

For such probabilistic generalisations estimated on corpus data, there has always been an interest in correlating the results with results from experimental work (for example, \citealp{ArppeJaervikivi2007,BresnanEa2007,BresnanFord2010,DivjakGries2008,DivjakEa2016,FordBresnan2013}).
This often called a \textit{validation} of the corpus-derived findings, but \citet[303]{Divjak2016} criticises this choice of words \textit{because it creates the impression that behavioral experimental data is inherently more valuable than textual data}, citing \cite{TummersEa2005}, who state that a corpus is \textit{a sample of spontaneous language use that is} (\textit{generally}) \textit{realized by native speakers}.
This position, which I adopt by and large, does not, however, imply that we can in some way \textit{deduce mental representations from patterns of use}, \ie\ from corpus data \citep[486--487]{Dabrowska2016}.%
\footnote{I suggest that the word \textit{induce} would be more appropriate than \textit{deduce}.}
In fact, it would be surprising if we could!
Nobody assumes that we can induce mental representations from experiments, which -- as opposed to corpus studies -- even provide a direct access to the cognitive agent and offer much better options to control and experimental conditions and nuisance variables.
Instead, a theory of cognitive representation is pre-specified, and predictions are derived from this theory \textit{before} the experiment or the corpus study is conducted.
Technical problems of statistical inference aside (but see Section~\ref{sec:rightstatistics}), a successful experiment corroborates the theory, and a failed experiment weakens the theory.

That said, the present study is conducted within the general paradigm of cognitive corpus linguistics and includes a comparison of the corpus findings with results from two experiments.
As a theoretical framework, I assume a model of similarity-based classification in the sense of Prototype Theory.
The approach within cognitive corpus linguistics (\eg\ \citealp{DivjakArppe2013,Gries2003}) assumes that the variables annotated in a corpus study on an alternation phenomenon define prototypes for the alternating variants.
The similarity of a given feature vector (in a concrete sentence where one of the variants is used) determines to a large extent which variant is chosen by speakers.
This entails that a variant of Prototype Theory with \textit{features} is assumed \citep{Rosch1978}, instead of the monolithic prototypes assumed in earlier versions.
While Prototype Theory is well suited for modeling constructional choices, it is just one similarity-based framework, the most prominent other framework being Exemplar Theory (\citealp{MedinSchaffer1978,Hintzman1986}; see \citealp{StormsEa2000} for a comparison of the theories in experimental settings).
Prototype Theory and Exemplar Theory differ mainly in whether they assume higher-level abstractions as part of the cognitive representation (Prototype Theory) or not (Exemplar Theory).
I am sceptical whether corpus analysis alone could ever decide which theory is more adequate, given that substantial doubt has been voiced whether even experimental methods are ultimately able to do so \citep{Barsalou1990}.%
\footnote{In \cite{DivjakArppe2013}, a fruitful attempt was made to show how both models form a converging picture based on corpus data.}
Prototype Theory (with feature abstractions) is simply preferred here because it fits the established alternation modeling paradigm, which relies on features being weighted (in a sense) in statistical models.
In Section~\ref{sec:analyses}, a prototype-theoretical parlance is therefore adopted.

@@

\subsection{A word on statistical analysis}
\label{sec:rightstatistics}

In this section, I motivate the choice of statistical models which I use later in Section~\ref{sec:corpusstudies}.
Readers might think that the method used here for modeling grammatical alternations -- namely (Hierarchical) Logistic Regression\slash Generalised Linear (Mixed) Models or GLM(M)s -- does not require much motivation.
After all, GLMMs have been established as the major tool in the analysis of alternation phenomena.
All studies mentioned at the outset of Section~\ref{sec:cogocl} use GLM(M)s \citep{BresnanEa2007,BresnanHay2010,BresnanFord2010,DivjakArppe2013,Gries2015,NessetJanda2010}.
Over the past few years, however, modified or alternative methods have been proposed.
From among these methods, I just make a few remarks on Bayesian estimation (see \citealp{GelmanEa2014}), as it was proposed in \cite{Levshina2016,Divjak2016a}.
Conceptually, I see three points of discussion that should be kept apart.
First, Bayesian methods are sometimes touted as superior tools for scientific inference compared to frequentist methods.
Second, it has been proposed that the Bayesian interpretation of probability is more cognitively adequate for the modeling of linguistic data.
Third, and very specific to this paper, given established methods in the modeling of alternation and variation, it has to be decided whether so-called Bayesian methods lead to substantially different results.

As for the first question, this is not quite the place to discuss it fully.
The basic distinction is a philosophical one and related to the concepts of \textit{direct} and \textit{inverse probability} (\eg\ \citealp{Senn2011}).
Frequentists assume that models and parameters are fixed, for example a model specifying that a coin is fair.
We can then calculate for observed data (for example a measurement of $3$ heads in an experiment with $10$ tosses) how often such a result or a more extreme result would occur if the model were true and we repeated the experiment arbitrarily often.
This is essentially the frequentist notion of direct probability, \ie\ long-run frequencies under replication.
Standard tests in the Fisher and Neyman-Pearson traditions as well as Neyman confidence intervals are based on this notion.
Bayesian approaches (in the now commonly found interpretation), on the other hand, condition on the particular data and quantify inductively the probability of model parameters given the data.
The parameters are thus not fixed, and the probability is usually equated with researchers' posterior beliefs about model parameters.
There is actually a debate among Bayesians about the proper interpretation of Bayesian methods, and whether a notion of hypothesis testing is compatible (or even already contained) in the Bayesian approach.
In \citet[10]{GelmanShalizi2013}, the authors -- prominent Bayesians themselves -- acknowledge that a theory of testing is a desideratum, and they state about the standard inductive interpretation of Bayesianism that \textit{most of this received view of Bayesian inference is wrong}, and they develop a Bayesian notion of p values (see also \citealp{Mayo2013}, for a frequentist reply; also \citealp{Senn2011} on different strands of Bayesianism and their stance on inductive vs.\ deductive reasoning).
Clearly, in such quarrels between and among camps of philosophers of science and statisticians it is difficult for mere practitioners to take sides.

These quarrels relate to the second question, however.
\citet[301--302]{Divjak2016a} speaks favourably of Bayesian methods because the Bayesian concept of probability is more adequate for cognitive modeling compared to the frequentist one.
Her argument is part of a larger body of literature asking for cognitively plausible modeling techniques, for example Naive Discriminative Learning (NDL; \citealp{Baayen2011,BaayenEa2013,MilinEa2016,TheijssenEa2013}).
Yet, neither frequentist nor Bayesian methods were conceived as cognitive models, but as systems of inference for researchers (see above, and see also \citealp[302]{Divjak2016a}).
The fundamental question that lurks behind such arguments is how we interpret our statistical models (estimated on corpus data).
Are they inductive models of cognitive representations that learners would infer from being exposed to the corpus data?%
\footnote{In which case we are doing \textit{data science in language research} in the words of \citealp{MilinEa2016}.}
Or are they tests of theories that are pre-specified and merely tested for predictive accuracy on linguistic output data contained in corpora.
In the former case, we adopt a strong \textit{corpus as input} hypothesis and should definitely resort to methods like NDL.
However, this would most likely require us to toss most previous work done in (cognitive) linguistics into the bin and abandoning all high-level generalisations that most existing studies have been based upon.
In fact, arguments to this extreme effect and against using high-level generalisation have been made, for example in \cite{BaayenEa2016}, \citet[299--300]{Divjak2016a}, \cite{RamscarPort2016}, \cite{TheijssenEa2013}.
In the latter and less extreme case, the cognitive commitment does, however, not necessarily extend to the statistical methods used.
These methods then do not need to be any more cognitively plausible than an ANOVA used to analyse the results from an experiment.
I view my own work (see Sections~\ref{sec:germanmeasurenps}--\ref{sec:experimental}) in the tradition of testing theories that embrace high-level generalisations, and I agree to provisionally use Likelihood methods (see below).
I remain fully agnostic with respect to the question which approach is `right'.
The best strategy for cognitive linguistics as a field might be to cultivate many methods while making sure that each method is applied carefully and competently.

@@

@@

Remarkably, however, she does \textit{not} use informative priors, and in her footnote 8 \cite[252]{Levshina2016} admits that priors were probed using trial and error, such that the proclaimed advantage of Bayesian modeling was apparently not taken advantage of.%

@@

MLE, like inductive Bayesianism, conditions on the data in as much as it searches for the most likely set of parameters given the data.

@@

However, most similar studies (back to \citealp{BresnanEa2007}) use an estimator (MLE) that is not frequentist, and most likely as cognitively plausible as Bayesian estimators.
If for Levshina's study, results did, in fact, \textit{not} converge, it would have been an ideal occasion to demonstrate the superiority of the algorithms used in Bayesian estimation.

@@

This section briefly reviews existing analyses of the \PGCa vs.\ \NACa\ alternation and related issues.
I also develop my own analysis and the appropriate hypotheses for the empirical studies presented in Sections~\ref{sec:corpusstudies} and \ref{sec:experimental}.
I discuss four main aspects:
first, the different syntactic structures of the variants \NACa\ and \PGCa\ in relation to their syntactic prototypes \NACb\ and \PGCd;
second, degrees of grammaticalisation of the measure noun associated with the two prototypes;
third, a semantic prototypicality effect of the degrees of grammaticalisation (preference to occur with cardinals);
fourth, preferences in different registers.

@@

The variables \textit{Kindattraction} and \textit{Measureattraction} encode the ratio with which a given kind noun lemma or measure noun lemma occurs in the \NACb\ and the \PGCd.
They were calculated from the auxiliary samples described at the end of Section~\ref{sec:gettingdata} as a log-transformed quotient.
The higher the value, the more often the noun occurs in the \PGCa (proportionally).%
\footnote{
  It could be argued that some more advanced measure of attraction strength should be used, as is done in Collostructional (or Collexeme) Analysis \citep{GriesStefanowitsch2004}, see also \cite{Gries2015a}.
  Three main points speak against such an approach in the present case (but see \citealp[246--249]{Levshina2016} for a successful more refined approach).
  First, the attraction values will be used as regressors in a GLMM, and the values resulting from collostructional approaches, \ie\ logarithmised Fisher p values, have a very unfavourable distribution in the case at hand.
  They cluster around $0$, and they include values of $-\infty$.
  Second, their main use in collostructional analyses is to \textit{sort} a list of collexemes and interpret their order.
  Their concrete numerical value might not have a solid cognitive interpretation in the given context.
  Third, I tried using collexeme strength as a regressor, and the results were unsatisfactory.
}
Additionally, \textit{Kindfreq} and \textit{Measurefreq} are the logarithm-transformed frequencies per 1,000,000 words of each lemma, extracted from the frequency lists distributed by the DECOW corpus creators on their web page.
They were added to control for basic frequency effects.

@@

The coefficient estimates are specified in Table~\ref{tab:bigtable} for each regressor (or regressor level) in the columns labelled \textit{Coefficient}.
For a robust quantification of the precision of the estimation, I ran a parametric bootstrap (using the \mbox{\textit{confint.merMod}} function from \textit{lme4}) with $1,000$ replications, and using the percentile method for the calculation of the intervals.
The resulting 95\% bootstrap confidence intervals are reported in Table~\ref{tab:bigtable} in the columns labelled \textit{CI low} and \textit{CI high} (= upper and lower 2.5th percentiles).
The column \textit{CI contains 0} shows an asterisk for those intervals that do \textit{not} include 0.
Furthermore, for each regressor, a $p$ value was obtained by dropping the regressor from the full model, re-estimating the nested model and comparing it to the full model.
Instead of inexact Wald approximations or Likelihood Ratio Tests, I used a drop-in bootstrap replacement for the Likelihood Ratio Test from the function \textit{PBmodcomp} from the \textit{pbkrtest} package \citep{HalekohHojsgaard2014}, hence I call the corresponding value $p_{\text{PB}}$.
These bootstrapped $p$ values are given in the columns labelled p\Sub{PB} in Table~\ref{tab:bigtable}.
Only \textit{Kindfreq} ($\mpPB=0.095$) can be seen as slightly too high to be convincing (non-significant).

@@

\subsection{Preliminary remarks}

In the two experiments reported in this section, I use probabilities for the alternating constructions calculated for attested material, and I correlate these probabilities with the participants' reactions.
Thus, a direct link can be established between output material found in corpora and the behaviour of linguistic agents.
The first experiment tests preferences for constructions explicitly.
\cite{FordBresnan2013} use the \textit{split-100} task in which participants have to distribute $100$ points between the alternatives, assigning more points to more natural sounding alternative.
In essence, participants distribute a probability mass between two variants, which is intended to produce more subtle results compared to what is essentially a two-alternative forced-choice task \cite{Rosenbach2013}.
The split-100 paradigm has been criticised in \cite{ArppeJaervikivi2007}, reiterated in \cite{DivjakEa2016}.
In \cite{VerhoevenTemme2017}, it was shown that results from forced-choice and split-100 experiments mostly converge, which is expected in the long run if a probability is turned into a binary decision.
I present a forced-choice experiment in Section~\ref{sec:exp:fc} and not a split-100 experiment, mainly because in a dry-run of the experiment, participants complained about the unnaturalness of the task of assigning a probability mass to two variants.
The analysis compares the probabilities assigned to stimuli by the corpus-derived model with the frequency with which participants chose the variants for the same stimuli.

\subsection{Experiment 1: forced choice}
\label{sec:exp:fc}

As was pointed out in Section \ref{sec:cogocl}, there is a strong interest in combining corpus-based findings with experiments.
Therefore, this section and the next present the results of two experiments wherein I compare results from the corpus study with experimental results.
Both experiments use sentences containing attested MNPs from the corpus sample (embedded into simplified sentences) as stimuli.
Also, the probabilities that the corpus-based model assigns to the two variants in these sentences is used as the main regressor in both studies.
First, a forced-choice experiment was conducted.
Participants had to chose between two sentences differing only in that one contained the \NACa\ and the other contained the \PGCa.

@@

A certain amount of the variance can be accounted for by idiosyncrasies of single sentences ($\sigma_{\text{Sentence}}=1.785$, $\sigma^{\text{Modelprediction}}_{\text{Sentence}}=5.996$, $16$ levels).%
\footnote{I use $\sigma^f_r$ to denote the standard deviation of the of the random intercepts for the fixed effect $f$ varying by random effect $r$.}
Also, among participants, there are clearly different preferences ($\sigma_{\text{Participant}}=0.781$, $\sigma^{\text{Modelprediction}}_{\text{Participant}}=0.484$, $24$ levels).
On the extreme sides, one participant chose the \PGCa\ in $13$ of $16$ cases, and two participants only chose it in $5$ of $16$ cases.
The regressor \textit{Modelprediction} achieves $\mpPB=0.007$ ($1,000$ replications) and is estimated at $5.408$ relative to an intercept of $-1.304$.
The confidence interval from a parametric bootstrap ($1,000$ replications, percentile method) for the regressor is acceptable but slightly large with a lower bound of $1.626$ and an upper bound of $8.397$.
Nakagawa \& Schielzeth's pseudo-coefficients of determination are $R^2_{m}=0.227$ and $R^2_{c}=0.561$, which means that over 22\% of the variance in the data can be explained by considering only the predictions from the corpus-based GLMM.
The effect display for the single fixed regressor \textit{Modelprediction} is given in Figure \ref{fig:afc:effects}.
The result is very clear.
The higher the probability of the \PGCa\ predicted from usage-data, the more often participants chose the \PGCa\ variant in the forced-choice task.
In summary, the forced choice experiment clearly succeeded in corroborating the results from the corpus study in as much as the preferences extracted from usage data correspond to native speakers' choices.

@@

Finally, I report the results of a self-paced reading experiment also designed to test whether the statistical model derived from usage data (see Section~\ref{sec:corpushierarchicalmodel}) can be used to predict speakers' behaviour.
I used exactly the same stimuli as in the forced choice experiments.
Each participant read both the $16$ sentences with the variant predicted by the corpus model and the $16$ modified sentences with the variant that the corpus model does not predict.%
\footnote{Notice that lemmas and their frequencies as well as lemma classes are included as regressors in the corpus-based GLMM, and there was consequently no additional controlling of lemma frequencies, etc.}
To minimise repetition effects, the stimuli for each participant were separated into two blocks of $16$ targets and $33$ fillers per block.
In the experiment, participants first read all sentences from the first block, then all sentences from the second block.
It was made sure that from each target sentence pair, one sentence was assigned to the first block, and the other sentence to the other block.
The assignment of members of the individual sentence pairs to the blocks was randomised for each participant individually, and so was the order within each block.
The sentences from each pair of variants were kept as far apart as possible.
The fillers also came in pairs such that the second block exclusively contained sentences to which participants had been exposed in the first block in slightly modified form.
In total, each participant read $98$ sentences.
After each sentence, participants had to answer simple (non-metalinguistic) yes-no questions about the previous sentence as distractors.
The distractor questions were different ones in the first and the second block.
There were $38$ (different) participants recruited in exactly the same manner as for the experiment reported in Section~\ref{sec:exp:fc}.
None of them had ever participated in any kind of reading experiment.
The experiment was conducted using \textit{PsychoPy}.

>>>>

  \author*[1]{Roland Schäfer}
  %\runningauthor{...}
  \affil[1]{Freie Universität Berlin}
  \title{Competing Constructions for German Measure Noun Phrases: from Usage Data to Experiment}
  \runningtitle{Competing Constructions for German Measure Noun Phrases}
  %\subtitle{...}
  \abstract{}
  \keywords{corpus methods and experimental methods, self-paced reading, forced-choice, alternations, hierarchical models, measure constructions, German}
  %\classification[PACS]{...}
  %\communicated{...}
  %\dedication{...}
  %\received{...}
  %\accepted{...}
  \journalname{(submitted)}
  \journalyear{2017}
  %\journalvolume{...}
  %\journalissue{...}
  %\startpage{...}
  %\aop
  %\DOI{...}

@@

For such probabilistic generalisations estimated on corpus data, there has always been an interest in correlating the results with results from experimental work (for example, \citealp{ArppeJaervikivi2007,BresnanEa2007,BresnanFord2010,DivjakGries2008,DivjakEa2016,FordBresnan2013}).
This often called a \textit{validation} of the corpus-derived findings, but \citet[303]{Divjak2016a} criticises this choice of words \textit{because it creates the impression that behavioral experimental data is inherently more valuable than textual data}, citing \cite{TummersEa2005}, who state that a corpus is \textit{a sample of spontaneous language use that is} (\textit{generally}) \textit{realized by native speakers}.
This position, which I adopt by and large, does not, however, imply that we can in some way \textit{deduce mental representations from patterns of use}, \ie\ from corpus data \citep[486--487]{Dabrowska2016}.%
\footnote{I suggest that the word \textit{induce} would be more appropriate than \textit{deduce}.}
In fact, it would be surprising if we could!
Nobody assumes that we can induce mental representations from experiments, which -- as opposed to corpus studies -- even provide a direct access to the cognitive agent and offer much better options to control and experimental conditions and nuisance variables.
Instead, a theory of cognitive representation is pre-specified, and predictions are derived from this theory \textit{before} the experiment or the corpus study is conducted.
Technical problems of statistical inference aside (but see Section~\ref{sec:rightstatistics}), a successful experiment corroborates the theory, and a failed experiment weakens the theory.
The simplest assumption would be that the same approach is adequate for corpus studies.

That said, the present study is conducted within the general paradigm of cognitive corpus linguistics and includes a comparison of the corpus findings with results from two experiments.
As a theoretical framework, I assume a model of similarity-based classification in the form of Prototype Theory.
The approach within cognitive corpus linguistics (\eg\ \citealp{DivjakArppe2013,Gries2003}) assumes that the variables annotated in a corpus study on an alternation phenomenon define prototypes for the alternating variants.
The similarity of a given feature vector (in a concrete sentence where one of the variants is used) determines to a large extent which variant is chosen by speakers.
This entails that a variant of Prototype Theory with \textit{features} is assumed \citep{Rosch1978}, instead of the monolithic prototypes assumed in earlier versions.
While Prototype Theory is well suited for modeling constructional choices, it is just one similarity-based framework, the most prominent other framework being Exemplar Theory (\citealp{MedinSchaffer1978,Hintzman1986}; see \citealp{StormsEa2000} for a comparison of the theories in experimental settings).
Prototype Theory and Exemplar Theory differ mainly in whether they assume higher-level abstractions as part of the cognitive representation (Prototype Theory) or not (Exemplar Theory).
I am sceptical that corpus analysis alone could ever decide which theory is more adequate, given that substantial doubt has been voiced whether even experimental methods are ultimately able to do so \citep{Barsalou1990}.%
\footnote{In \cite{DivjakArppe2013}, a fruitful attempt was made to show how both models form a converging picture based on corpus data.}
Prototype Theory (with feature abstractions) is simply preferred here because it fits the established alternation modeling paradigm, which relies on features being weighted (in a sense) in statistical models.
In Section~\ref{sec:analyses}, a prototype-theoretical parlance is therefore adopted.

@@

\subsection{On statistical analysis}
\label{sec:rightstatistics}

In this section, I motivate the choice of statistical models which I use later in Section~\ref{sec:corpusstudies}.
Readers might think that the method used here for modeling grammatical alternations -- namely (Hierarchical) Logistic Regression\slash Generalised Linear (Mixed) Models or GLM(M)s -- does not require much motivation.
After all, GLMMs have been established as the major tool in the analysis of alternation phenomena.
All studies mentioned at the outset of Section~\ref{sec:cogocl} use GLM(M)s \citep{BresnanEa2007,BresnanHay2010,BresnanFord2010,DivjakArppe2013,Gries2015,NessetJanda2010} use some form of regression\slash GLM(M).
Over the past few years, however, modified or alternative methods have been proposed.
From among these methods, I just make a few remarks on Bayesian estimation (see \citealp{GelmanEa2014}), as it was proposed in \cite{Levshina2016,Divjak2016a}, for example.
Conceptually, I see three points of discussion that should be kept apart.
First, Bayesian methods are sometimes touted as superior tools for scientific inference compared to frequentist methods.
Second, it has been proposed that the Bayesian interpretation of probability is more cognitively adequate for the modeling of linguistic data.
Third, and very specific to this paper, given established methods in the modeling of alternation and variation, it has to be decided whether so-called Bayesian methods lead to substantially different results.

As for the first question, this is not quite the place to discuss it fully.
The basic distinction is a philosophical one and related to the concepts of \textit{direct} and \textit{inverse probability} (\eg\ \citealp{Senn2011}).
Frequentists assume that models and parameters are fixed, for example a model specifying that a coin is fair.
We can then calculate for observed data (for example a measurement of $3$ heads in an experiment with $10$ tosses) how often such a result or a more extreme result would occur if the model were true and we repeated the experiment arbitrarily often.
This is essentially the frequentist notion of direct probability, \ie\ long-run frequencies under replication.
Standard tests in the Fisher and Neyman-Pearson traditions as well as Neyman confidence intervals are based on this notion.
Bayesian approaches (in the now common interpretation), on the other hand, condition on the particular data and quantify inductively the probability of model parameters given the data.
The parameters are thus not fixed, and the probability is usually equated with researchers' posterior beliefs about model parameters.
There is actually a debate among Bayesians about the proper interpretation of Bayesian methods, and whether a notion of hypothesis testing is compatible (or even already contained) in the Bayesian approach.
In \citet[10]{GelmanShalizi2013}, the authors -- prominent Bayesians themselves -- acknowledge that a theory of testing is a desideratum, and they state about the standard inductive interpretation of Bayesianism that \textit{most of this received view of Bayesian inference is wrong}, and they develop a Bayesian notion of $p$ values (see also \citealp{Mayo2013}, for a frequentist reply; also \citealp{Senn2011} on different strands of Bayesianism and their stance on inductive vs.\ deductive reasoning).
Clearly, in such quarrels between and among camps of philosophers of science and statisticians it is difficult for mere practitioners to take sides.

These quarrels relate to the second question, however.
\citet[301--302]{Divjak2016a} speaks favourably of Bayesian methods because the Bayesian concept of probability is more adequate for cognitive modeling compared to the frequentist one.
Her argument is part of a larger body of literature asking for cognitively plausible modeling techniques, for example Naive Discriminative Learning (NDL; \citealp{Baayen2011,BaayenEa2013,MilinEa2016,TheijssenEa2013}). 
On p.\ 303 of \cite{Divjak2016a}, the author explicitly mentions NDL.
Yet, neither frequentist nor Bayesian methods were conceived as cognitive models, but as systems of inference for scientists (see above, and see also \citealp[302]{Divjak2016a}).
The fundamental question that lurks behind such arguments is how we interpret our statistical models (estimated on corpus data).
Are they inductive models of cognitive representations that also human learners would infer from being exposed to the corpus data?%
\footnote{In which case we are doing \textit{data science in language research} in the words of \citealp{MilinEa2016}.}
Or are they tests of theories that are pre-specified and merely tested for predictive accuracy on linguistic output data contained in corpora.
In the former case, we adopt a strong \textit{corpus as input} hypothesis and should definitely resort to methods like NDL.
However, this would most likely require us to toss most previous work done in (cognitive) linguistics into the bin and abandoning all high-level generalisations that most existing studies have been based upon.
In fact, arguments to this extreme effect and against using high-level generalisation have been made, for example in \cite{BaayenEa2016}, \citet[299--300]{Divjak2016a}, \cite{RamscarPort2016}, \cite{TheijssenEa2013}.
In the latter and less extreme case, the cognitive commitment does, however, not necessarily extend to the statistical methods used.
These methods then do not need to be any more cognitively plausible than an ANOVA used to analyse the results from an experiment.
I view my own work (see Sections~\ref{sec:germanmeasurenps}--\ref{sec:experimental}) in the tradition of testing theories that embrace high-level generalisations, and I agree to provisionally use Likelihood methods (see below).
I remain fully agnostic with respect to the question which approach is `right'.
The best strategy for cognitive linguistics as a field might be to cultivate many methods while making sure that each method is applied carefully and competently.

@@

Also, especially Neyman-style frequentism has well-known extensions to estimation (see \citealp{GreenlandEa2016}, esp.\ p.\ 340).

@@

Remarkably, given this statement, she does \textit{not} use informative priors, and in her footnote 8 \cite[252]{Levshina2016} admits that priors were probed using trial and error.
So, the proclaimed major advantage of Bayesian modeling was apparently not taken advantage of.%

@@

MLE, like inductive Bayesianism, conditions on the data in as much as it searches for the most likely set of parameters given the particular data.

@@

However, most similar studies (back to \citealp{BresnanEa2007}) use an estimator (MLE) that is not frequentist, and as cognitively plausible as Bayesian estimators because it most likely produces the same results in these studies.
If for Levshina's study, results from Bayesian and MLE methods did, in fact, \textit{not} converge, it would have been an ideal occasion to demonstrate the superiority of the algorithms used in Bayesian estimation.

@@

This section briefly reviews existing analyses of the \PGCa vs.\ \NACa\ alternation and related issues.
I also develop my own analysis and the appropriate hypotheses for the empirical studies presented in Sections~\ref{sec:corpusstudies} and \ref{sec:experimental}.
I discuss four main aspects:
first, the different syntactic structures of the variants \NACa\ and \PGCa\ in relation to their syntactic prototypes \NACb\ and \PGCd;
second, degrees of grammaticalisation of the measure noun associated with the two prototypes;
third, a semantic prototypicality effect of the degrees of grammaticalisation (a preference to occur with cardinals);
fourth, preferences in different registers.

@@

The variables \textit{Kindattraction} and \textit{Measureattraction} encode the ratio with which a given kind noun lemma or measure noun lemma occurs in the \NACb\ and the \PGCd.
They were calculated from the auxiliary samples described at the end of Section~\ref{sec:gettingdata} as a log-transformed quotient.
The higher the value, the more often the noun occurs in the \PGCa (proportionally).%
\footnote{
  It could be argued that some more advanced measure of attraction strength should be used, as is done in Collostructional (or Collexeme) Analysis \citep{GriesStefanowitsch2004}, see also \cite{Gries2015a}.
  Three main points speak against such an approach in the present case (but see \citealp[246--249]{Levshina2016} for a successful more refined approach).
  First, the attraction values will be used as regressors in a GLMM, and the values resulting from collostructional approaches, \ie\ logarithmised Fisher $p$ values, have a very unfavourable distribution in the case at hand.
  They cluster around $0$, and they include values of $-\infty$.
  Second, their main use in collostructional analyses is to \textit{sort} a list of collexemes and interpret their order.
  Their concrete numerical value might not have a solid cognitive interpretation in the given context.
  Third, I tried using collexeme strength as a regressor, and the results were unsatisfactory.
}
Additionally, \textit{Kindfreq} and \textit{Measurefreq} are the logarithm-transformed frequencies per 1,000,000 words of each lemma, extracted from the frequency lists distributed by the DECOW corpus creators on their web page.
They were added to control for basic frequency effects.

@@

The coefficient estimates are specified in Table~\ref{tab:bigtable} for each regressor (or regressor level) in the columns labelled \textit{Coefficient}.
For a robust quantification of the precision of the estimation, I ran a parametric bootstrap (using the \mbox{\textit{confint.merMod}} function from \textit{lme4}) with $1,000$ replications, and using the percentile method for the calculation of the intervals.
The resulting 95\% bootstrap confidence intervals are reported in Table~\ref{tab:bigtable} in the columns labelled \textit{CI low} and \textit{CI high} (= upper and lower 2.5th percentiles).
The column \textit{CI contains 0} shows an asterisk for those intervals that do \textit{not} include 0.
Furthermore, for each regressor, a $p$ value was obtained by dropping the regressor from the full model, re-estimating the nested model and comparing it to the full model.
Instead of inexact Wald approximations or Likelihood Ratio Tests, I used a drop-in bootstrap replacement for the Likelihood Ratio Test from the function \textit{PBmodcomp} from the \textit{pbkrtest} package \citep{HalekohHojsgaard2014}.
I call the corresponding value $p_{\text{PB}}$, and it is given in the appropriately labeled columns in Table~\ref{tab:bigtable}.
Only \textit{Kindfreq} ($\mpPB=0.095$) can be seen as slightly too high to be convincing (non-significant).

@@

\subsection{Experiment 1: forced-choice}
\label{sec:exp:fc}

In the two experiments reported in this section, I use probabilities for the alternating constructions calculated for attested material, and I correlate these probabilities with the participants' reactions.
Thus, a direct link can be established between output material found in corpora and the behaviour of linguistic agents (see also Section~\ref{sec:cogocl}).
Both experiments use sentences containing attested MNPs from the corpus sample (embedded into simplified sentences) as stimuli.
Also, the probabilities that the corpus-based model assigns to the two variants in these sentences is used as the main regressor in both studies.

The first experiment tests preferences for constructions explicitly.
\cite{FordBresnan2013} use the \textit{split-100} task in which participants have to distribute $100$ points between the alternatives, assigning more points to more natural sounding alternative.
In essence, participants distribute a probability mass between two variants, which is intended to produce more subtle results compared to a two-alternative forced-choice task \cite{Rosenbach2013}, where participants have to choose one of two variants.
The split-100 paradigm has been criticised in \cite{ArppeJaervikivi2007}.
The criticism was reiterated in \cite{DivjakEa2016}, where they use a forced-choice task.
In \cite{VerhoevenTemme2017}, it was shown that results from forced-choice and split-100 experiments mostly converge, which is expected in the long run if a probability is turned into a binary decision.
I present a forced-choice experiment in Section~\ref{sec:exp:fc} and not a split-100 experiment, mainly because in a dry-run of the experiment, participants complained about the unnaturalness of the task of distributing a probability mass across two variants.
Participants had to chose between two sentences differing only in that one contained the \NACa\ and the other contained the \PGCa.
The analysis compares the probabilities assigned to stimuli by the corpus-derived model with the frequency with which participants chose the variants for the same stimuli.

@@

A certain amount of the variance can be accounted for by idiosyncrasies of single sentences ($\sigma_{\text{Sentence}}=1.785$, $\sigma^{\text{Modelprediction}}_{\text{Sentence}}=5.996$, $16$ levels).%
\footnote{I use $\sigma^f_r$ to denote the standard deviation of the of the random intercepts for the fixed effect $f$ varying by random effect $r$.}
Also, among participants, there are clearly different preferences ($\sigma_{\text{Participant}}=0.781$, $\sigma^{\text{Modelprediction}}_{\text{Participant}}=0.484$, $24$ levels).
On the extreme sides, one participant chose the \PGCa\ in $13$ of $16$ cases, and two participants only chose it in $5$ of $16$ cases.
The regressor \textit{Modelprediction} achieves $\mpPB=0.007$ ($1,000$ replications) and is estimated at $5.408$ relative to an intercept of $-1.304$.
The confidence interval from a parametric bootstrap ($1,000$ replications, percentile method) for the regressor is acceptable but slightly large with a lower bound of $1.626$ and an upper bound of $8.397$.
Nakagawa \& Schielzeth's pseudo-coefficients of determination are $R^2_{m}=0.227$ and $R^2_{c}=0.561$, which means that over 22\% of the variance in the data can be explained by considering only the predictions from the corpus-based GLMM.
The effect display for the single fixed regressor \textit{Modelprediction} is given in Figure \ref{fig:afc:effects}.
The result is very clear.
The higher the probability of the \PGCa\ predicted from usage-data, the more often participants chose the \PGCa\ variant in the forced-choice task.
In summary, the forced-choice experiment clearly succeeded in corroborating the results from the corpus study in as much as the preferences extracted from usage data correspond to native speakers' choices.

@@

Conretely, the exact same stimuli as in the forced-choice experiments were used.
Each participant read both the $16$ sentences with the variant predicted by the corpus model and the $16$ modified sentences with the variant that the corpus model does not predict.%
\footnote{Notice that lemmas and their frequencies as well as lemma classes are included as regressors in the corpus-based GLMM, and there was consequently no additional controlling of lemma frequencies, etc.}
To minimise repetition effects, the stimuli for each participant were separated into two blocks of $16$ targets and $33$ fillers per block.
In the experiment, participants first read all sentences from the first block, then all sentences from the second block.
It was made sure that from each target sentence pair, one sentence was assigned to the first block, and the other sentence to the other block.
The assignment of members of the individual sentence pairs to the blocks was randomised for each participant individually, and so was the order within each block.
The sentences from each pair of variants were kept as far apart as possible.
The fillers also came in pairs such that the second block exclusively contained sentences to which participants had been exposed in the first block in slightly modified form.
In total, each participant read $98$ sentences.
After each sentence, participants had to answer simple (non-metalinguistic) yes-no questions about the previous sentence as distractors.
The distractor questions were different ones in the first and the second block.
There were $38$ (different) participants recruited in exactly the same manner as for the experiment reported in Section~\ref{sec:exp:fc}.
None of them had ever participated in any kind of reading experiment, and none of them took part in the first experiment (and vice versa).
The experiment was conducted using \textit{PsychoPy}.
